%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Mrs. Jane Smith \\


%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Jerin Roberts \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2165 Westsyde rd. \\ Kamloops, BC b2b 7c3 \\ (250) 682-6536 % Your address and phone number
\end{center} 
\vfill

\signature{Jerin Roberts} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To Whom this May Concern,} 

My Goal is to become an assistant researcher within the prestigious organization of SNOLAB, while learning and gaining experience for my future goal of pursuing a career in Particle Physics. I am a 4th year Physics Major at Thompson Rivers University and know my background and experience will allow me to be an asset to your organization.
I have completed a number of projects involving delicate, technical design and precise assembly. For a directed studies project I designed and professionally constructed operational sensors for a high altitude balloon using a LPKF circuit milling machine and Eagle CAD drafting software. The circuits included a GPS telemetry transmitter and receiver, a cosmic radiation detector, accelerometer and atmospheric sensors all designed as Arduino shields. The Project required a great deal of patience and analytical debugging. This experience combined with my education and hardworking nature will be a valuable asset to SNOLAB.
Summer 2013 I received an undergraduate research award (UREAP) from Thompson Rivers University in which I re-designed and fabricated RFID sensing equipment for animal detection. The project involved managing a \$1000 budget and working with biological researchers to technically design and construction more than 25 circuit boards using surface mounted technology. The project required a great deal of patience and attention to detail in order to assure all units were precisely milled, assembled and tested to exceed the requirements outlined by the client.  The project required a large amount of work with programing PIC’s which I know combined with my experience with C++ and other languages will be of great value to SNOLAB.

I hope to hear from you soon to discuss how I can become a valued member of your organization.  I look forward to starting my researching career, as well as pursuing opportunities for professional development and advancement within SNOLAB. Thank you for your kind consideration of my qualifications.  

\closing{Sincerely yours,}


\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}